---
title: "DATA1901"
format: 
  html:
    embed-resources: true
    code-fold: true
editor: visual
---

# Executive Summary

# Initial Data Analysis

Source, structure, reclassification, limitation of data collection, assumptions, define meaning of key variables, describe any assumption (idea about the data), data cleaning.

```{r}
library(readxl)
sheets = excel_sheets("all_data.xlsx")
print(sheets)
```

```{r}
all_data = read_excel("all_data.xlsx", sheet = sheets[5])
head(all_data)
```

```{r}
library(dplyr)

data = all_data %>% select(age, gender, env, choice, BSSQ_5, ASSQ_5)
head(data)
```

```{r}
mutated_data = mutate(data, focus_lvl_diff = ASSQ_5 - BSSQ_5)
head(mutated_data)
```

```{r}
filtered_data <- filter(mutated_data, gender != 'Other')
head(filtered_data)
```

cleaning: data row yang gender other remove

# Research Questions

## Research Question 1

```{r}
library(tidyverse)

ggplot(filtered_data, aes(x=age, y=focus_lvl_diff)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x="Age",
       y="Difference in Focus Level",
       title="Age vs ∆ Focus") 
```

```{r}
library(ggplot2)
library(plotly)

p = ggplot(filtered_data, aes(x=age, y=focus_lvl_diff, colour = gender)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x="Age",
       y="Difference in Focus Level",
       title="Age vs ∆ Focus") 

ggplotly(p)
```

```{r}
p = ggplot(mutated_data, aes(x=age, y=focus_lvl_diff, colour = env)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x="Age",
       y="Difference in Focus Level",
       title="Age vs ∆ Focus") 

ggplotly(p)
```

```{r}
ggplot(mutated_data, aes(x=age, y=focus_lvl_diff, colour = choice)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x="Age",
       y="Difference in Focus Level",
       title="Age vs ∆ Focus") 
```

```{r}
library(ggplot2)

# Fitting the model
model = lm(focus_lvl_diff ~ age, data = mutated_data)

# Create a residual plot
ggplot(model, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "red") +
  labs(title = "Residuals vs. Fitted Values")
```

```{r}
filtered_snowy = filter(mutated_data, env == 'Snowy')
filtered_sunny = filter(mutated_data, env == 'Sunny')
```

```{r}
model_snowy = lm(focus_lvl_diff ~ age, data = filtered_snowy)

# Create a residual plot
ggplot(model_snowy, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "red") +
  labs(title = "Residuals vs. Fitted Values")
```

```{r}
model_sunny = lm(focus_lvl_diff ~ age, data = filtered_sunny)

# Create a residual plot
ggplot(model_sunny, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "red") +
  labs(title = "Residuals vs. Fitted Values")
```

how to plot the residual for both models? should we make two different tables?

## Research Question 2

# Articles

2 articles max 50 words

# Acknowledgement

# References

```{r}
library(readxl)
sheets = excel_sheets("all_data.xlsx")
print(sheets)
```

```{r}
all_data = read_excel("all_data.xlsx", sheet = sheets[5])
head(all_data)
```

::: panel-tabset
## header 1

```{r}
library(dplyr)

data = all_data %>% select(age, BSSQ_5, ASSQ_5)
head(data)
```

```{r}
mutated_data = mutate(data, focus_lvl_diff = ASSQ_5 - BSSQ_5)
head(mutated_data)
```

## header 2

*very important* **No**

-   bullet
-   bullet

```{r}
library(tidyverse)
# ggplot(mutated_data, aes(x=age, y=focus_lvl_diff, colour = gender)) +
  #geom_point() + 
  #geom_smooth(method = "lm", se = FALSE) + 
  #labs(x="Age",
   #    y="Difference in Focus Level",
    #   title="Age vs ∆ Focus") 
```
:::

```{r}
library(ggplot2)


# Fitting the model
model = lm(focus_lvl_diff ~ age, data = mutated_data)

# Create a residual plot
ggplot(model, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "red") +
  labs(title = "Residuals vs. Fitted Values")
```

```{r}
ggplot(mutated_data, aes(x=age)) + geom_histogram()
```

```{r}
ggplot(mutated_data, aes(x=focus_lvl_diff)) + geom_bar()
```

just say that lm isn't the perfect fit for the data. Dive deeper to the data, look into journals abt the correlation you're researching.

how the effect of using vr
