---
title: "DATA1901"
format: 
  html:
    embed-resources: true
    code-fold: true
editor: visual
---

# Executive Summary

# Initial Data Analysis

Source, structure, reclassification, limitation of data collection, assumptions, define meaning of key variables, describe any assumption (idea about the data), data cleaning.

```{r}
library(readxl)
sheets = excel_sheets("all_data.xlsx")
print(sheets)
```

```{r}
all_data = read_excel("all_data.xlsx", sheet = sheets[5])
head(all_data)
```

```{r}
library(dplyr)

data = all_data %>% select(age, env, BSSQ_5, ASSQ_5)
head(data)
```

```{r}
library(tidyverse)
mutated_data = mutate(data, focus_lvl_diff = ASSQ_5 - BSSQ_5)

mutated_data = na.omit(mutated_data)
head(mutated_data)
```

# Research Questions

```{r}
ggplot(mutated_data, aes(x = age)) + 
  geom_histogram(aes(y = after_stat(density)), bins = 15, color = "red", fill = "orange") +
  stat_function(fun = dnorm, 
                args = list(mean = mean(mutated_data$age), sd = sd(mutated_data$age)))
```

```{r}
ggplot(mutated_data, aes(x=BSSQ_5)) + geom_bar()
ggplot(mutated_data, aes(x=ASSQ_5)) + geom_bar()
```

```{r}
ggplot(mutated_data, aes(x=focus_lvl_diff)) + geom_bar()
```

```{r}
library(RColorBrewer)

Pie1=select(mutated_data, env)
data_agg <- Pie1 %>%
  count(env)

colors <- brewer.pal(n = length(unique(Pie1$env)), name = "Blues")

fig <- plot_ly(data_agg, labels = ~env, values = ~n, type = 'pie', marker = list(colors = colors))
fig <- fig %>% layout(title = 'Distribution of Environment',
                      showlegend = TRUE)
fig
```

## Research Question 1

```{r}
library(tidyverse)

ggplot(mutated_data, aes(x=age, y=focus_lvl_diff)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x="Age",
       y="Difference in Focus Level",
       title="Age vs ∆ Focus") 
```

```{r}
library(ggplot2)

# Fitting the model
model = lm(focus_lvl_diff ~ age, data = mutated_data)

# Create a residual plot
ggplot(model, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "red") +
  labs(title = "Residuals vs. Fitted Values")
```

```{r}
library(ggplot2)
library(plotly)
p = ggplot(mutated_data, aes(x=age, y=focus_lvl_diff, colour = env)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x="Age",
       y="Difference in Focus Level",
       title="Age vs ∆ Focus") 

ggplotly(p)
```

```{r}
filtered_snowy = filter(mutated_data, env == 'Snowy')
filtered_sunny = filter(mutated_data, env == 'Sunny')
```

```{r}
model_snowy = lm(focus_lvl_diff ~ age, data = filtered_snowy)

# Create a residual plot
ggplot(model_snowy, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "red") +
  labs(title = "Residuals vs. Fitted Values")
```

```{r}
model_sunny = lm(focus_lvl_diff ~ age, data = filtered_sunny)

# Create a residual plot
ggplot(model_sunny, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "red") +
  labs(title = "Residuals vs. Fitted Values")
```

## Research Question 2

# Articles

2 articles max 50 words

# Acknowledgement

# References

::: panel-tabset
## header 1

```{r}
library(dplyr)

data = all_data %>% select(age, BSSQ_5, ASSQ_5)
head(data)
```

```{r}
mutated_data = mutate(data, focus_lvl_diff = ASSQ_5 - BSSQ_5)
head(mutated_data)
```

## header 2

*very important* **No**

-   bullet
-   bullet

```{r}
library(tidyverse)
# ggplot(mutated_data, aes(x=age, y=focus_lvl_diff, colour = gender)) +
  #geom_point() + 
  #geom_smooth(method = "lm", se = FALSE) + 
  #labs(x="Age",
   #    y="Difference in Focus Level",
    #   title="Age vs ∆ Focus") 
```
:::

just say that lm isn't the perfect fit for the data. Dive deeper to the data, look into journals abt the correlation you're researching.

how the effect of using vr
